\documentclass[10pt]{article}
\title{Math 1551, Differential Calculus Worksheets}
\author{}

% LOAD PACKAGES
\usepackage{amsmath} % allows for align env and other things
\usepackage{graphicx} % allows for graphics
\usepackage{textcomp} % allows for single apostrophe
\usepackage{enumitem} % allows for alpha lettering in enumerated lists
\usepackage{amsfonts} % for real numbers symbol and other sets
\usepackage[mathscr]{euscript} % Euler script font
\usepackage{wrapfig} % to allow text wrapping
\usepackage{pgfplots} % for tikz graphics

% FONT FORMAT
\renewcommand*\rmdefault{ppl} % change font to Palatino

% MARGINS
\usepackage{anysize}
\marginsize{2.5cm}{2.5cm}{2cm}{3cm}

% SHORTCUTS
\newcommand{\Textbook}{Thomas 13$^{th}$ Edition}
\newcommand{\Sections}{Sections from \Textbook: }


\newcommand{\SolutionsStatement}{As stated in the syllabus, a goal of this course is to prepare students for more advanced courses that have this course as a pre-requisite. To help us meet this goal, the solutions that are provided for worksheets only give what you would need to write in a quiz, midterm or exam. This is intentional: upper level math courses often don't have recitations, let alone worksheets and worksheet solutions. So students need, develop, and use various strategies to check their solutions in those courses. \\[6pt]

In this course, students are encouraged to ask questions they may have about the course on Piazza, office hours, by checking their answers with their peers, or by asking their instructor after class or over email. Calculators and software are also great ways to check your work. All of these methods are valuable skills that are transferable to higher level courses.}

\newcommand{\Course}{Math 1551}
\newcommand{\Semester}{Spring 2017}
\newcommand{\TorF}{Indicate whether the statement true or false. If it is true, in one or two sentences, explain why. If false, give a counter example or explain why in one or two sentences.}

\newcommand{\TorFShort}{Indicate whether the statement true or false. Explain your reasoning.}

% OTHER
\newcommand{\R}{{\mathbb R}} % The real numbers
\newcommand{\Emph}[1]{\textbf{#1}} % Emphasize

% DERIVATIVES
\newcommand{\dfdx}{\frac{df}{dx}}
\newcommand{\dfdt}{\frac{df}{dt}}
\newcommand{\ddx}{\frac{d}{dx}}
\newcommand{\ddt}{\frac{d}{dt}}
\newcommand{\dxdt}{\frac{dx}{dt}}
\newcommand{\dydt}{\frac{dy}{dt}}

% FANCY HEADERS
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhf{}
%\date{}
%\lhead{Please print first and last names: }
%\rhead{Worksheet for \thesection\hspace{0.25cm}}

%\usepackage{lastpage} % for fancy page numbering
%\rfoot{Page \thepage \hspace{1pt} } %of \pageref{LastPage}}

% REMOVE FIRST LINE INDENTATION 
\setlength\parindent{0pt}


% ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ 
\begin{document}
%\input{FrontPage.tex}

%\setcounter{section}{05}


%\input{worksheets/ws01.tex}
%\input{worksheets/ws01s.tex}

%\input{worksheets/ws02.tex}
%\input{worksheets/ws02s.tex}

%\input{worksheets/ws03.tex}
%\input{worksheets/ws03s.tex}

%\input{worksheets/ws04.tex}
%\input{worksheets/ws04s.tex}

%\input{worksheets/ws05.tex}
%\input{worksheets/ws05s.tex}

%\input{worksheets/ws06.tex}
%\input{worksheets/ws06s.tex}

%\input{worksheets/ws07.tex}
%\input{worksheets/ws07s.tex}

%\input{worksheets/ws08.tex}
%\input{worksheets/ws08s.tex}

%\input{worksheets/ws09.tex}
%\input{worksheets/ws09s.tex}

%\input{worksheets/ws10.tex}
%\input{worksheets/ws10s.tex}

\input{worksheets/ws11.tex}
\input{worksheets/ws11s.tex}



\end{document}
