\newpage\section*{Worksheet 1, \Course, \Semester} 
\noindent \Sections 1.1, 1.2, 1.3

\subsection*{Welcome to Math 1551 Recitation!} 
    
    Recitations are meant for students to complete additional exercises, with a TA and other students, on topics recently covered in lecture. Recitations are meant to be
    \begin{itemize}
        \item active: students should be solving exercises themselves during recitations
        \item collaborative: students are encouraged to work together during recitation, to present their solutions on the board, and to ask for help from the TA
    \end{itemize}

Each worksheet provides exercises for one recitation.
    \begin{itemize}
        \item There may not be time in recitation to complete all exercises. 
        \item Students are expected to be able to solve all worksheet exercises.
    \end{itemize}
    
    Students are also encouraged to seek help from TAs, their instructor, and other students if they have any questions on any of the worksheet exercises. All questions are numbered, so students can more easily refer to them outside of recitation, in Piazza, in office hours, and so on.

\subsection*{Background Review}
\begin{itemize}
	\item \emph{Function $y = f(x)$}: a rule that assigns each value of $x$ to exactly one value of $y$.
	\item \emph{Domain of a function $f(x)$}: all the values that $x$ can have. 
	\item \emph{Range of a function $f(x)$}: all the values that $f(x)$ can have. 
	\item \emph{Composite function}: we define $(f \circ g)(x) = f (g(x))$.
\end{itemize}

You should be able to graph the functions below.
\vspace{-6pt}
\begin{center}
	\def\arraystretch{1.5}
    \begin{tabular}{ p{3cm} p{3cm} p{3cm} p{6cm} }
        $y = mx + b$ & $y = x^2$ & $y = x^3$ & $y=x^n$, $n$ any integer \\
        $y = |x|$ & $y=\sqrt{x}$ & $\sqrt{1 - x^2}$ & $\frac{1}{x}$\\
        $\sin x$ & $\cos x$ & $\tan x$ & $\csc x$ \\
        $\sec x$ & $\cot x$ 
    \end{tabular}
\end{center}

You should also be able to graph transformations of the above functions. Recall the following basic transformations:
\begin{itemize}
	\item \emph{Vertical shift}: $y = f(x) + c$ shifts up or down $c$ units
    \item \emph{Horizontal shift}: $y = f (x - c)$ shifts left or right $c$ units.
    \item \emph{Reflections}: $y = −f(x)$ reflects about the $x$-axis and $y = f(−x)$ reflects about the $y$-axis. 
    \item \emph{Stretching/Compressing}: $y = af(x)$ stretches when $|a| > 1$ and compresses when $0 < |a| < 1$; $y = f(bx)$ stretches when $0 < |b| < 1$ and compresses when $|b| > 1$.
\end{itemize}

\newpage
\subsection*{Trigonometric Identities}

Pythagorean Identities

$$\sin^2 x + \cos^2 x = 1, \qquad 1 + \tan^2 x = \sec^2 x, \qquad 1 + \cot^2 x = \csc^2 x$$

Half-Angle Formulas
$$\sin^2 x = \frac{1}{2}[1 - \cos(2x)] , \qquad \cos^2 x = \frac{1}{2} [1 + \cos(2x)] $$

Double-Angle Formulas
$$\sin(2x) = 2 \sin x \cos x $$ $$ \cos(2x) =\cos^2 x - \sin^2 x = 1 - 2 \sin^2 x
= 2 \cos^2 x - 1$$

Angle Sum and Difference
$$\sin (x \pm y) = \sin x \cos y \pm \sin y \cos x $$ 
$$\cos (x \pm y) = \cos x \cos y \mp \sin y \sin x $$

\subsection*{Exercises}

\begin{enumerate}
	\item Identify the domain and range of the following functions and sketch them. 
    \begin{enumerate}
    	\item $\displaystyle{f(u) = \sqrt{25 - u^2}-1}$
        \item $g(t) = t^2 -8t + 3$
        \item $A(x) = \begin{cases} 
      \displaystyle{1+\frac{1}{x-1}} & x\leq 0 \\[8pt]
      \displaystyle{\sqrt{4 - x^2}} & 0 < x\leq 2 \\
   \end{cases}$
    \end{enumerate}
	\item Given that $\sec \theta = -\sqrt{2}$, and that $\theta \in [\pi,3\pi/2]$, compute the values of the other five trig functions.
    \item If possible, give at least one example of a function for each of the following cases.
    \begin{enumerate}
    	\item A function that is decreasing for all values of $x$ and whose range is the interval $(0,\infty)$.
        \item A non-constant even function whose range is the interval $[0,1]$.
        \item A function, $f(x)$, so that $f \circ g = (x+3)(x-3)$, where $g = x^2 - 10$.
    \end{enumerate}
    \item Express $y(t)$ as a single sine function $y(t) = \frac{\sqrt{3}}{2}\cos(t) + \frac{1}{2}\sin(t)$
    \item Find all values of $\theta$ that satisfy $\sin2\theta-\cos\theta = 0$.
\end{enumerate}